 ---
title: "Graph network analysis"
output:
  html_document: default
  html_notebook: default
---

## load libraries and set path
```{r}
suppressPackageStartupMessages({
  library(igraph)
  library(ggplot2)
  library(dplyr)
})

setwd("C:/Users/abhinav/Documents/blockchain project")
```

## Data import
```{r}
blockdata.df1 <- read.csv("output/blockchain_info_sample3.csv")
blockdata.df2 <- read.csv("output/blockchain_info_sample.csv")
blockdata.df3 <- read.csv("output/blockchain_info_sample_150001_200000.csv")
blockdata.df4 <- read.csv("output/blockchain_info_sample_50001_100000.csv")
blockdata.df <- rbind(blockdata.df1,blockdata.df2,blockdata.df3,blockdata.df4)
blockdata.df <- blockdata.df[,c('ip_add', 'op_add', 'ip_value', 'op_value', 'time' )]

rm(list = c('blockdata.df1','blockdata.df2','blockdata.df3','blockdata.df4'))
```


##search for Silk road address in data
```{r}
##address length checks
nchar('1F1tAaz5x1HUXrCNLbtMDqcw6o5GNn4xqX')
nchar(as.character(blockdata.df$ip_add[1]))

'1F1tAaz5x1HUXrCNLbtMDqcw6o5GNn4xqX' %in% as.character(blockdata.df$ip_add)

```


## make a list of addresses as nodes
```{r}
blockdata.nodes<- data.frame(unique(c(as.character(blockdata.df$ip_add), as.character(blockdata.df$op_add))))
colnames(blockdata.nodes) <- c("nodes")
```

## changing addresses to integer ids
```{r}
start <- proc.time()
blockdata.nodes$ad_id <- c(1:nrow(blockdata.nodes))
temp_df <-merge(blockdata.df, blockdata.nodes, by.x= "ip_add", by.y = "nodes", suffixes = c("",".from"))
temp_df <-merge(blockdata.df, blockdata.nodes, by.x= "ip_add", by.y = "nodes")
temp_df <- merge(temp_df, blockdata.nodes, by.x= "op_add", by.y = "nodes")
cat(sprintf("--- elapsed user-time: %fs ", (proc.time() - start)[1]))
```

```{r}
temp_df <- temp_df[,c('ad_id.x', 'ad_id.y', 'ip_value', 'op_value', 'time' )]
colnames(temp_df) <- c('from_id', 'to_id', 'ip_value', 'op_value', 'time')
```


## create graph from dataframe
```{r}
start <- proc.time()
blockdata.graph <- graph_from_data_frame(temp_df,directed = TRUE,vertices = blockdata.nodes$ad_id)
   cat(sprintf("--- elapsed user-time: %fs ", (proc.time() - start)[1]))
   
```
--34mb

## Simplify the graph by removing loops and multiple edges between the same nodes
```{r}
start <- proc.time()
blockdata.graph <- simplify(blockdata.graph, remove.multiple = T, remove.loops = T, 
edge.attr.comb=c(weight="sum", type="ignore") )
   cat(sprintf("--- elapsed user-time: %fs ", (proc.time() - start)[1]))
```
--15mb

## setting vertex and edges properties for plots
```{r}
V(blockdata.graph)$color <- "grey"
E(blockdata.graph)$color <- "grey"
E(blockdata.graph)$color[as.logical(blockdata.graph[,5])]<- "red"
V(blockdata.graph)[degree(blockdata.graph, mode = "out")>4]$color <-  "yellow"
```

## creating a subgraph with high degree nodes
```{r}
blockdata.subgraph <- subgraph(blockdata.graph, degree(blockdata.graph, mode = "out")>4)
blockdata.subgraph <- subgraph(blockdata.subgraph, degree(blockdata.subgraph, mode = "in")>4)

```

## Interactive plotting (computationally inefficient)
```{r}
#start <- proc.time()
#tkplot(blockdata.graph, vertex.label = NA,vertex.size = 1, edge.arrow.size = 0.1)
#   cat(sprintf("--- elapsed user-time: %fs ", (proc.time() - start)[1]))
  
```

## simple plotting
```{r}
start <- proc.time()
plot(blockdata.subgraph, vertex.label = NA,vertex.size = 0.1, edge.arrow.size = 0.1 )
   cat(sprintf("--- elapsed user-time: %fs ", (proc.time() - start)[1]))
  
```


##Community detection based on edge betweenness
```{r}
block.community <- cluster_edge_betweenness(blockdata.subgraph)
#dendPlot(block.community, mode="hclust")
```


```{r}
class(block.community)
#length(block.community)
#membership(block.community)
modularity(block.community)
#crossing(block.community, blockdata.graph)
```

```{r}
plot(block.community, blockdata.subgraph,vertex.label = NA,vertex.size = 1, edge.arrow.size = 0.1 )
```

##Community detection based on based on propagating labels

```{r}
#block.community.prop <- cluster_label_prop(blockdata.graph)
#plot(block.community.prop, blockdata.graph)
```



```{r}
#scc<- clusters(blockdata.graph,"strong")
#clusters with more than one vertex
#v_idx <- which(scc$csize > 1)
#unique(as.vector(graph[,1:2]))[scc$membership==v_idx[2]]
```


#clustering coefficient
```{r}
start <- proc.time()
blockdata.graph.cc <- transitivity(blockdata.subgraph, type = c("local"), vids = blockdata.nodes$ad_id)
cat(sprintf("--- elapsed user-time: %fs ", (proc.time() - start)[1]))

```

#between centrality
```{r, message=FALSE, include=FALSE}
start <- proc.time()
blockdata.graph.btwnscore <- estimate_betweenness(blockdata.subgraph, vids = V(blockdata.nodes$ad_id), directed = TRUE, 5, weights = NULL, nobigint = TRUE)
```

The vertex and edge betweenness are (roughly) defined by the number of shortest paths going through a vertex or an edge.





